---
title: "p8105_hw6_hg2596"
output: github_document
date: "2022-11-29"
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(p8105.datasets)
library(dplyr)
library(corrplot)
library(plotly)
library(modelr)
library(mgcv)

set.seed(1)
```

# Problem 2 

```{r}
homicide_1= read_csv("./data/homicide_data.csv", show_col_types = FALSE)
```

# Creating a City State Variable 

```{r}
homicide_1 = homicide_1 %>%
  unite('city_state', city:state, remove = FALSE) %>% 
  apply(., 2, function(city_state) as.character(gsub("_", ",", city_state))) 

```

The homicide raw data has `r nrow(homicide_1) ` observations and `r ncol(homicide_1)`  variables. 
Key variables are **uid** which gives a unique ID to each homicide victim and the **city**, **state** in which the killing took place. Another important variable is the **deposition** which describes the status of the case for examples is it closed with an arrest or possibly still open with no arrest. 

# Cleaning Data and Creating Status Variable 

```{r}
homicide_2 = as_tibble(homicide_1) %>%
  janitor::clean_names() %>%
  mutate(victim_age = as.numeric(victim_age)) %>%
  mutate(lat = as.numeric(lat)) %>%
  mutate(lon = as.numeric(lon)) %>%
  mutate(status = ifelse(disposition%in%c("Closed by arrest"), 1, 0))
```


# omit variable and Filter Out and Race

```{r}
homicide_3 = 
  homicide_2 %>%
  mutate(omitt = ifelse(city_state%in%c("Dallas,TX","Phoenix,AZ","Kansas City,MO","Tulsa,AL"), 0, 1)) %>%
  filter(omitt == 1) %>%
  filter(victim_race %in% c("White","Black")) %>%
  arrange(status)
  
```

# Filter out Baltimore and Logisitic Reg

```{r}
fit_logistic = 
  homicide_3 %>% 
  filter(city_state == "Baltimore,MD") %>%
  glm(status ~ victim_age + victim_sex + victim_race, data = ., family = binomial()) 

```

```{r}
fit_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate), 
         CI_Lower = exp((estimate) - 1.96*(std.error)),
         CI_Upper = exp((estimate) + 1.96*(std.error))) %>%
  select(term, log_OR = estimate, OR, CI_Lower, CI_Upper, p.value) %>%
  knitr::kable(digits = 3)
```

#Filter out Vicitm Sex Unknown 

```{r}
homicide_4 = 
  homicide_3 %>%
  filter(victim_sex %in% c("Female","Male"))
```

# Map over cities 

```{r}
fit_over_cities = 
  homicide_4 %>%
  nest(data = -city_state) %>%
  mutate(
    models = map(data, ~glm(status ~ victim_age + victim_sex + victim_race, data = .x, family = binomial()) %>% broom::tidy()%>%
         mutate(OR = exp(estimate), 
         CI_Lower = exp((estimate) - 1.96*(std.error)),
         CI_Upper = exp((estimate) + 1.96*(std.error))) %>%
  filter(term == "victim_sexMale") %>%
  select(term, OR, CI_Lower, CI_Upper, p.value) %>%
  knitr::kable(digits = 3))) %>%
  unnest(models) %>%
  select(-data) 


fit_over_cities
```

# Problem 3 

```{r}
birth= read_csv("./data/birthweight.csv", show_col_types = FALSE)
```

# Clean Data 

```{r}
birth_wt = 
  birth %>%
  janitor::clean_names() %>%
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace), 
         mrace = as.factor(mrace))

```

# Take away Character Varaibles for the Cor Matrix 

```{r}
birth_cor =
  birth_wt %>%
  select(-babysex,-frace,-mrace)
```

# Create a Correlation Matrix 

```{r}
M = cor(birth_cor)
corrplot(M, method = 'color', order = 'alphabet')
```

Based on correlation matrix, the predictors that have the highest correlation with the outcome **birth weight** are **bhead** and **blenght**.

```{r}
birth_2 = 
  birth_wt %>%
  select(bwt,bhead,blength)
```

# Create Linear Regression 

```{r}
l1 = 
  lm(bwt ~ bhead + blength, data = birth_2)
  
```

# Add Residuals and Predictors 

```{r}
birth_3 = 
  birth_2 %>% 
  add_residuals(l1) %>%
  add_predictions(l1)

birth_3

```

# Plot residuals and fitted values for L1 

```{r}
graph_1 = 
  birth_3 %>%
  plot_ly(x = ~pred, y = ~resid, type = "scatter", mode = "markers",alpha = 1.2) %>% 
  layout(title = 'Residuals vs Fitted Values (Graph 1)',
         xaxis = list(title = 'Fitted Values'),
         yaxis = list(title = 'Residuals'), 
         legend = list(title=list(text='<b> True Mean Values </b>'))) 

graph_1
```

# Create Second Linear Regression 

```{r}
l2 = 
  lm(bwt ~ blength + gaweeks, data = birth_wt)

second_set = 
  birth_wt %>% 
  select(bwt, blength, gaweeks) %>%
  add_residuals(l2) %>%
  add_predictions(l2)

second_set
```

# Graph 2

```{r}
graph_2 = 
  second_set %>%
  plot_ly(x = ~pred, y = ~resid, type = "scatter", mode = "markers",alpha = 1.2) %>% 
  layout(title = 'Residuals vs Fitted Values (Graph 2)',
         xaxis = list(title = 'Fitted Values'),
         yaxis = list(title = 'Residuals'), 
         legend = list(title=list(text='<b> True Mean Values </b>'))) 

graph_2
```

# Create Third Linear Regression 

```{r}
l3 = 
  lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = birth_wt)

third_set = 
  birth_wt %>% 
  select(bwt,bhead,blength,babysex) %>%
  add_residuals(l3) %>%
  add_predictions(l3)

third_set
```

# Graph 3 

```{r}
graph_3 = 
  third_set %>%
  plot_ly(x = ~pred, y = ~resid, type = "scatter", mode = "markers",alpha = 1.2) %>% 
  layout(title = 'Residuals vs Fitted Values (Graph 3)',
         xaxis = list(title = 'Fitted Values'),
         yaxis = list(title = 'Residuals'), 
         legend = list(title=list(text='<b> True Mean Values </b>'))) 

graph_3
```

# Check with Cross Validation 

```{r}
cv_df =
  crossv_mc(birth_wt, 100)

```

```{r}
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

```

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    linear_m  = map(train, ~lm(bwt ~ bhead + blength, data = .x)),
    linear_m2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    linear_m3 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x))) %>% 
  mutate(
    rmse_linear_1 = map2_dbl(linear_m, test, ~rmse(model = .x, data = .y)),
    rmse_linear_2    = map2_dbl(linear_m2, test, ~rmse(model = .x, data = .y)),
    rmse_linear_3 = map2_dbl(linear_m3, test, ~rmse(model = .x, data = .y)))

cv_df
```

# Show the RMSE 

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

