---
title: "p8105_hw6_hg2596"
output: html_document
date: "2022-11-29"
---

```{r}
library(tidyverse)
library(p8105.datasets)
```

# Problem 2 

```{r}
homicide_1= read_csv("./data/homicide_data.csv", show_col_types = FALSE)
```

# Creating a City State Variable 

```{r}
homicide_1 = homicide_1 %>%
  unite('city_state', city:state, remove = FALSE) %>% 
  apply(., 2, function(city_state) as.character(gsub("_", ",", city_state))) 

```

The homicide raw data has `r nrow(homicide_1) ` observations and `r ncol(homicide_1)`  variables. 
Key variables are **uid** which gives a unique ID to each homicide victim and the **city**, **state** in which the killing took place. Another important variable is the **deposition** which describes the status of the case for examples is it closed with an arrest or possibly still open with no arrest. 

# Cleaning Data and Creating Status Variable 

```{r}
homicide_2 = as_tibble(homicide_1) %>%
  janitor::clean_names() %>%
  mutate(victim_age = as.numeric(victim_age)) %>%
  mutate(lat = as.numeric(lat)) %>%
  mutate(lon = as.numeric(lon)) %>%
  mutate(status = ifelse(disposition%in%c("Closed without arrest","Open/No arrest"), 1, 0))
```

```{r}
fit_logistic = 
  homicide_2 %>% 
  glm(status ~ victim_age + victim_sex + victim_race, data = ., family = binomial()) 
```

```{r}
fit_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate)) %>%
  select(term, log_OR = estimate, OR, p.value) %>% 
  knitr::kable(digits = 3)
```

# Do it for each of the cities (

grouping 
piping 
purr::map (need to create function!)
)

# Problem 3 

```{r}
birth= read_csv("./data/birthweight.csv", show_col_types = FALSE)

```

```{r}
head(birth)
```

```{r}
birth_wt = 
  birth_wt %>%
  janitor::clean_names() %>%
  mutate(babysex = as.character(babysex),
         frace = as.character(frace), 
         mrace = as.character(mrace))

```

```{r}
head(birth_wt)
```

