---
title: "p8105_hw6_hg2596"
output: github_document
date: "2022-11-29"
editor_options: 
  chunk_output_type: inline
---

```{r}
library(tidyverse)
library(p8105.datasets)
library(dplyr)
library(corrplot)
library(plotly)
library(modelr)
library(mgcv)

set.seed(1)
```

### Problem 1

To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 


# Problem 2 

```{r}
homicide_1= read_csv("./data/homicide_data.csv", show_col_types = FALSE)
```

# Creating a City State Variable 

```{r}
homicide_1 = homicide_1 %>%
  unite('city_state', city:state, remove = FALSE) %>% 
  apply(., 2, function(city_state) as.character(gsub("_", ",", city_state))) 

```

The homicide raw data has `r nrow(homicide_1) ` observations and `r ncol(homicide_1)`  variables. 

# Cleaning Data and Resolved Variable 

```{r}
homicide_2 = as_tibble(homicide_1) %>%
  janitor::clean_names() %>%
  mutate(victim_age = as.numeric(victim_age)) %>%
  mutate(lat = as.numeric(lat)) %>%
  mutate(lon = as.numeric(lon)) %>%
  mutate(status = ifelse(disposition%in%c("Closed by arrest"), 1, 0))
```

# Clean up Data

```{r}
homicide_3 = 
  homicide_2 %>%
  mutate(omitt = ifelse(city_state%in%c("Dallas,TX","Phoenix,AZ","Kansas City,MO","Tulsa,AL"), 0, 1)) %>%
  filter(omitt == 1) %>%
  filter(victim_race %in% c("White","Black")) %>%
  arrange(status)
  
```

# Logisitic Regression for Baltimore

```{r}
fit_logistic = 
  homicide_3 %>% 
  filter(city_state == "Baltimore,MD") %>%
  glm(status ~ victim_age + victim_sex + victim_race, data = ., family = binomial()) 

```

# Table for OR and CI for Baltimore

```{r}
fit_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate), 
         CI_Lower = exp((estimate) - 1.96*(std.error)),
         CI_Upper = exp((estimate) + 1.96*(std.error))) %>%
  filter(term == "victim_sexMale") %>%
  select(term, OR, CI_Lower, CI_Upper, p.value) %>%
  knitr::kable(digits = 3)
```

#Filter out Vicitm Sex 'Unknown' 

```{r}
homicide_4 = 
  homicide_3 %>%
  filter(victim_sex %in% c("Female","Male"))
```

# Map Over all Cities 

```{r}
fit_over_cities = 
  homicide_4 %>%
  nest(data = -city_state) %>%
  mutate(
    models = map(data, ~glm(status ~ victim_age + victim_sex + victim_race, data = .x, family = binomial())),
                 outcome = map(models,broom::tidy,conf.int = TRUE)) %>%
      unnest(cols = outcome) %>%
      mutate(OR = exp(estimate), 
         CI_Lower = exp((estimate) - 1.96*(std.error)),
         CI_Upper = exp((estimate) + 1.96*(std.error))) %>%
   select(city_state, term, log_OR = estimate, OR, CI_Lower, CI_Upper, p.value) %>%
  filter(term == "victim_sexMale") %>%
  select(city_state,term,OR, CI_Lower, CI_Upper)
```

# Table of OR and CI for all Cities

```{r}
final = 
  fit_over_cities %>%
   knitr::kable(digits = 3)

final
```

# Graph Cities and OR 

```{r}

graph_p_1 = 
  fit_over_cities %>%
  mutate(city_state = fct_reorder(city_state, OR)) %>%
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() +
  geom_errorbar(aes(ymin = CI_Lower, ymax = CI_Upper)) + 
  labs(
    title = "Scatter Plot of OR Estimates with Error Bars",
    x = "Cities",
    y = "OR Estimates",
  ) + 
  theme(axis.text.x=element_text(angle=60,vjust = 1, hjust=1,size=10))

graph_p_1  
```

When we plot **estimated ORs** and **Cls** for each city, what we can observe that a majority of **OR** are below 1.There are only three cities that have an **OR** higher than 1 and those are **Fresno**, **Stockton** and **Albuquerque** so in these cities, a male victim of homicide has **1.5** times the odds of **the case being solved** then female victims, after adjusted for victim age and sex. In New York, a male victim of homicide has about **0.3** times the odds of **the case being solved** then female victims, after adjusted for victim age and sex. Whereas, Washington DC, a male victim of homicide has **0.7** times the odds of **the case being solved** then females victims, after adjusted for victim age and sex. Therefore, the odds of solving a case really depends on what city the victim was in, but it does seem to favor closing female victim cases over male victim cases. 


# Problem 3 

```{r}
birth= read_csv("./data/birthweight.csv", show_col_types = FALSE)
```

# Clean Birth Data 

```{r}
birth_wt = 
  birth %>%
  janitor::clean_names() %>%
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace), 
         mrace = as.factor(mrace))

```

# Take away Character Varaibles for the Cor Matrix 

```{r}
birth_cor =
  birth_wt %>%
  select(-babysex,-frace,-mrace)
```

# Create a Correlation Matrix 

```{r}
M = cor(birth_cor)
corrplot(M, method = 'color', order = 'alphabet')
```

Based on correlation matrix, the predictors that have the highest correlation with the outcome **birth weight** are **bhead** and **blenght**.

```{r}
birth_2 = 
  birth_wt %>%
  select(bwt,bhead,blength)
```

# Create Linear Regression 

```{r}
l1 = 
  lm(bwt ~ bhead + blength, data = birth_2)
  
```

# Add Residuals and Predictors 

```{r}
birth_3 = 
  birth_2 %>% 
  add_residuals(l1) %>%
  add_predictions(l1)

birth_3

```

# Graph 1: Plot residuals and fitted values for L1 

```{r}
graph_1 = 
  birth_3 %>%
  plot_ly(x = ~pred, y = ~resid, type = "scatter", mode = "markers",alpha = 1.2) %>% 
  layout(title = 'Residuals vs Fitted Values (Graph 1)',
         xaxis = list(title = 'Fitted Values'),
         yaxis = list(title = 'Residuals'), 
         legend = list(title=list(text='<b> True Mean Values </b>'))) 

graph_1
```

# Create Second Linear Regression 

```{r}
l2 = 
  lm(bwt ~ blength + gaweeks, data = birth_wt)

second_set = 
  birth_wt %>% 
  select(bwt, blength, gaweeks) %>%
  add_residuals(l2) %>%
  add_predictions(l2)

second_set
```

# Graph 2: Plot residuals and fitted values for L2

```{r}
graph_2 = 
  second_set %>%
  plot_ly(x = ~pred, y = ~resid, type = "scatter", mode = "markers",alpha = 1.2) %>% 
  layout(title = 'Residuals vs Fitted Values (Graph 2)',
         xaxis = list(title = 'Fitted Values'),
         yaxis = list(title = 'Residuals'), 
         legend = list(title=list(text='<b> True Mean Values </b>'))) 

graph_2
```

# Create Third Linear Regression 

```{r}
l3 = 
  lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = birth_wt)

third_set = 
  birth_wt %>% 
  select(bwt,bhead,blength,babysex) %>%
  add_residuals(l3) %>%
  add_predictions(l3)

third_set
```

# Graph 3: Plot residuals and fitted values for L3

```{r}
graph_3 = 
  third_set %>%
  plot_ly(x = ~pred, y = ~resid, type = "scatter", mode = "markers",alpha = 1.2) %>% 
  layout(title = 'Residuals vs Fitted Values (Graph 3)',
         xaxis = list(title = 'Fitted Values'),
         yaxis = list(title = 'Residuals'), 
         legend = list(title=list(text='<b> True Mean Values </b>'))) 

graph_3
```

# Check with Cross Validation 

```{r}
cv_df =
  crossv_mc(birth_wt, 100)

```

```{r}
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

```

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    linear_m  = map(train, ~lm(bwt ~ bhead + blength, data = .x)),
    linear_m2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    linear_m3 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x))) %>% 
  mutate(
    rmse_linear_1 = map2_dbl(linear_m, test, ~rmse(model = .x, data = .y)),
    rmse_linear_2    = map2_dbl(linear_m2, test, ~rmse(model = .x, data = .y)),
    rmse_linear_3 = map2_dbl(linear_m3, test, ~rmse(model = .x, data = .y)))

cv_df
```

# Show the RMSE 

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

It's important to note that **low RMSE** values are what help show if a model is a good fit. In our violin graph, it shows how **linear regression 1** and the **third regression** had similar range for rmse and were the lowest compared to the **second linear regression**.This goes to show that **including all the interaction terms** in the **third linear regression** were helpful in predicting the model compared to **length at birth** and **gestational age** which were not as good as a fit.It also makes since that the first model I created had a low RMSE because I knew that my predictors **blength** and **bhead** were **highly associated** with the outcome, therefore better at predicting the model. 



